\section{Introduction}
\label{sec:intro}

    Hardware design has become a very complex activity. The size of circuits has increased, while
    low-level concerns (power consumption, error correction, parallelization, layout, etc.) have to
    be incorporated earlier and earlier in the design process. This breaks modularity and makes it
    harder to validate and verify the correctness of circuits.

    In this context, researchers have been suggesting (since the 1980s) the usage of functional
    programming languages to model circuits. One particular line of research is to create Embedded
    Domain-Specific Languages for hardware description based on existing functional programming
    languages, such as Haskell.

    There are a multitude of EDSLs for hardware description, but they vary wildly on a number of
    aspects: host language, level of abstraction, capabilities of simulation, formal verification,
    synthesis (generation of netlists) and integration with other tools, to name a few. All this
    variety can make the task of choosing a hardware EDSL for the task at hand daunting and
    time-consuming.

    The main goal of this experimentation project is to establish some order in this landscape, and
    to perform a practical analysis of some popular functional hardware EDSLs. By reading the
    materials produced in this project (circuit models, test cases, generated netlists, report), a
    hardware designer wishing to use a functional hardware EDSL for his next design should gain some
    insight about the strengths and weaknesses of each language and have an easier time choosing
    one.

    As an additional result of this research, we intend to identify recent, cutting-edge
    developments in the Haskell language and its implementations from which the analyzed EDSLs could
    benefit. Also, we intend to discuss to which extent some shortcomings of the EDSLs could be
    overcome by having them hosted in a dependently-typed language.
